Multispecies survey for diet comp

### 2020-11-20 SurveyDietCompTest.Rmd
scaling diet and sampling with rdirichlet

sample_diet <- function(dat, fgs) {

  # dat can be long format output of load_diet_comp, or create_survey_diet, both have layers aggregated
  # load_diet_comp output has no polygon column and atoutput is proportion, 
  # create_survey_diet output has polygon column and atoutput is consumption in tons
  # first aggregate to get global diet comp in proportion, if not already in that form

@@

@@

  # then apply Dirichlet obs error; Dirichlet equivalent of rmultinom(1, effN, trueagecomp)?   
  # see e.g., https://rdrr.io/cran/DirichletReg/man/Dirichlet.html

>>>>

sample_diet <- function(dat, fgs, alphamult = 10000000) {

  # dat can be long format output of load_diet_comp, or create_survey_diet, both have layers aggregated
  # load_diet_comp output has no polygon column and atoutput is proportion, 
  # create_survey_diet output has polygon column and atoutput is consumption in tons
  # first aggregate to get global diet comp by species, agecl, time in proportion, if not already in that form

@@

  # aggregate over age? which ones? leave as age class specific?

@@

  # then apply Dirichlet obs error; Dirichlet equivalent of rmultinom(1, effN, trueagecomp)?   
  # see e.g., https://rdrr.io/cran/DirichletReg/man/Dirichlet.html
  # alpha vector is the diet comp scaled by a user-supplied multiplier
  # default to a very high multiplier for close-to-true diet comp
  # lower multipliers stray further from true diet comp

  # testdiet <- c(.1, .32, .06, .02, .49, .01)
  # library(DirichletReg)
  # rdirichlet(10, 10000000*testdiet)
  # rdirichlet(10, 100*testdiet)

  alphavec <- alphamult *

  sampdiet <- DirichletReg::rdirichlet(1, alphavec)
